Texture Mapping 3D Models of Indoor Environments with Noisy Camera Poses

### 2012-06-25 3dimpvt/paper.tex
nearly finished draft 4

\begin{figure}
  \centering
  \subfloat[][]{\includegraphics[width=3in]{projectionWall.jpg}}
  \centering
  \subfloat[][]{\includegraphics[width=3in]{projectionCeiling.jpg}}
  \caption{(a): Undistorted fisheye images for vertical planes such as
    walls are tilted, but their effective camera axis is more or less
    normal to the plane. (b): The effective camera axis for ceilings
    is at an angle with respect to the plane normal.}
  \label{fig:projectionAngles}
\end{figure}

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=3in]{pipelineimages.pdf}
  \caption{Textures corresponding to each step in our texture mapping
    pipeline.}
  \label{fig:pipelineimages}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=3in]{4thfloor21.jpg}
  \includegraphics[width=3in]{4thfloor61.jpg}
  \includegraphics[width=3in]{wall3final.jpg}
  \includegraphics[width=3in]{4thfloor8.jpg}
  \includegraphics[width=3in]{floorcropped.jpg}
  \includegraphics[width=3in]{fullmodel.png}
  \caption{Examples of our final texture mapping output for walls, a
    ceiling, an entire floor, as well as a fully textured model}
  \label{fig:results}
\end{figure}

@@

>>>>

\begin{figure}
  \centering
  \subfloat[][]{\includegraphics[width=1in]{projectionWall.pdf}}
  \centering
  \subfloat[][]{\includegraphics[width=1.1in]{projectionCeiling.pdf}}
  \centering
  \subfloat[][]{\includegraphics[width=0.9in]{projectionWallCrop.pdf}}
  \caption{(a): Undistorted fisheye images for vertical planes are tilted, but their effective camera axis is more or less
    normal to the plane. (b): The effective camera axis for ceilings
    is at an angle with respect to the plane normal. (c): Wall images are cropped to be rectangular.}
  \label{fig:projectionAngles}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=6in]{pipelineimages.pdf}
  \caption{Textures corresponding to each step in our texture mapping
    pipeline.}
  \label{fig:pipelineimages}
\end{figure*}

@@

@@

\begin{figure}
  \centering
  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}}

  \centering
  \subfloat[][]{\includegraphics[width=3in]{4thfloor8.jpg}}

  \centering
  \subfloat[][]{\includegraphics[width=3in]{floorcropped.jpg}}

  \centering
  \subfloat[][]{\includegraphics[width=3in]{fullmodel.png}}
  \caption{Examples of our final texture mapping output for (a) walls, (b) a
    ceiling, (c) an entire floor, (d) a full model}
  \label{fig:results}
\end{figure}

@@

\appendix
\section{Occlusion Masking}
\label{sec:occlusionMasking}
For the seam minimization process, we need to ensure that our images contain only content
that should be mapped onto the target plane in question. The tiling
approach only checks occlusion for each tile as it is
being textured. For seam minimization, entire images are used, so occlusion checks need to be performed over the entirety of each image to
determine available areas for texture mapping.

Fortunately, by virtue of our indoor environments, the vast majority
of surface geometry is either horizontal or vertical, with high
amounts of right angles. This means that after masking out occluded
areas, image projections will remain largely rectangular. We can
be efficient by recursively splitting each image into rectangular
pieces, and performing the same occlusion checks used in the tiling
process where needed. To occlude out rectangles, their texture is removed, as untextured areas are
never used for texture mapping.
